---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# povcalnetR

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/povcalnetR)](https://cran.r-project.org/package=povcalnetR)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/tonyfujs/povcalnetR.svg?branch=master)](https://travis-ci.org/tonyfujs/povcalnetR)
<!-- badges: end -->

The `povcalnetR` package allows R users to compute poverty and inequality indicators for more than 160 countries and regions from the World Bank's database of household surveys. It has the same functionality as the [PovcalNet website](http://iresearch.worldbank.org/PovcalNet/home.aspx). PovcalNet is a computational tool that allows users to estimate poverty rates for regions, sets of countries or individual countries, over time and at any poverty line.

PovcalNet is managed jointly by the Data and Research Group in the World Bank's Development Economics Division. It draws heavily upon a strong collaboration with the Poverty and Equity Global Practice, which is responsible for the gathering and harmonization of the underlying survey data.

## Installation

The development version can be installed from [GitHub](https://github.com/) with:

``` r
install.packages(c("devtools", "httr"))
devtools::install_github("tonyfujs/povcalnetR")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(povcalnetR)

## basic example code
povcalnet(country = c("ALB", "CHN"))
```

