---
title: "Helper functions and advanced examples"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{advanced_usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE, message=FALSE}
library(povcalnetR)
library(dplyr)
library(purrr)
```

## Specify parameters at the country level  
This function can be very handy is you maintain a list of countries and
parameters in a table like the one below.
_Note_: This function only works with survey years. There is no `fill_gaps` 
option available

```{r}
# Read values from a table
data("sample_input")
sample_input
```
```{r, message=FALSE, warning=FALSE}
# Use table values to send a request to the API
# Only works for survey years
povcalnet_cl(country = sample_input$country,
             povline = sample_input$poverty_line,
             year = sample_input$year,
             ppp = sample_input$ppp)
```

## Helper functions  
### Information table  

```{r, message=FALSE, warning=FALSE}
povcalnet_info() %>%
glimpse()
```

### Get all available countries from a World Bank region  

```{r, message=FALSE, warning=FALSE}
get_countries(c("ECA"))
```

### Get all available countries from a World Bank income classification  

```{r, message=FALSE, warning=FALSE}
get_countries(c("LIC"))
```

## Combining functions
### Pass different poverty lines to countries from different income groups  

```{r, message=FALSE, warning=FALSE}
income_groups <- c("LIC", "LMC", "UMC")
poverty_lines <- c(1.9, 3.2, 5.5)
map2_df(income_groups, poverty_lines, ~povcalnet(country = get_countries(.x),
                                                 povline = .y,
                                                 year = 2015,
                                                 aggregate = TRUE)
        )
```

