---
title: "povcalnetR"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{Get started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
NOT_CRAN <- identical(tolower(Sys.getenv("NOT_CRAN")), "true")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  purl = NOT_CRAN
)
```

```{r setup}
library(povcalnetR)
```
The `povcalnetR` package allows to easily query the [PovcalNet API](http://iresearch.worldbank.org/PovcalNet/docs/PovcalNet%20API.pdf) from R.

Here are a few examples to get you started:

## Using default options
By default, the `povcalnet` function return all available  

- countries  
- coverages (national, urban, rural)  
- for all available survey years  
- at the 1.9 USD poverty line  

```{r message=FALSE, warning=FALSE, eval=NOT_CRAN}
povcalnet()
```

## Basic options

### Filter by country
```{r, warning=FALSE, message=FALSE, eval=NOT_CRAN}
# Specify ONE country
povcalnet(country = "ALB")

# Specify MULTIPLE countries
povcalnet(country = c("ALB", "CHN"))
```

### Filter by year
By default, `povcalnet` will only return data if a survey is available for the
requested __country__ and the requested __year__
```{r, warning=FALSE, message=FALSE, eval=NOT_CRAN}
# Survey year NOT available
povcalnet(country = "ALB", year = 2012)

# Survey year NOT available - Empty response
povcalnet(country = "ALB", year = 2018)
```

### Modify the poverty line
```{r, warning=FALSE, message=FALSE, eval=NOT_CRAN}
povcalnet(country = "ALB", povline = 3.2)
```

## Other features

### Get estimates when survey year is not available
The `fill_gaps` argument will trigger the interpolation / extrapolation of 
poverty estimates when survey year is not available

```{r, warning=FALSE, message=FALSE, eval=NOT_CRAN}
# fill_gaps = FALSE (default)
povcalnet(country = "HTI")

# fill_gaps = TRUE
povcalnet(country = "HTI", fill_gaps = TRUE)
```

### Compute custom aggregates
The `povcalnet` function can also be used to compute aggregate welfare statistics
of custom group of countries

```{r, warning=FALSE, message=FALSE, eval=NOT_CRAN}
# World aggregate
povcalnet(country = "all", aggregate = TRUE)

# Custom aggregate
povcalnet(country = c("CHL", "ARG", "BOL"), aggregate = TRUE)
```
